Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2015-05-28 cordillera-cycle.tex
Add statement on min/max ice volumes in 5 km runs.

@@

@@

>>>>

During MIS~2, total ice volume peaks at 8.01\,m~s.l.e. in the GRIP simulation
and at 8.77\,m~s.l.e. in the EPICA simulation.

@@

During MIS~4, total ice volume peaks at 7.19\,m~s.l.e. in the GRIP simulation
and at 5.04\,m~s.l.e. in the EPICA simulation, corresponding to respectively
90 and 57\,\% of the MIS~2 ice volumes.

@@

During MIS~3, total ice volume corresponding to these persistent ice-dispersal
centres reaches a minimum of 1.52\,m~s.l.e. in the GRIP simulation and of
2.68\,m~s.l.e. in the EPICA simulation, corresponding to respectively 19 and
31\,\% of the MIS~2 ice volumes.
